DPIV Analysis and Real Time Implementation

### 2023-01-09 Paper/main.tex
small comment

The described algorithm was used to study how the hydrodynamic response of synthetic micro particles, i.e. silica beads, can be related to their physical properties and differ according to the fluid in which they are suspended. To compare the results obtained for the same kind of particles suspended in different fluids, the velocity signal $\mean{x}$ was computed per each experiment, by the DPIV-based algorithm described in \sect\ref{sec:method}.

>>>>

The described algorithm \DS{I'd stress the real-time properties of the algorithm. Therefore, "the real-time capabilities of the algorihtm have been used to"} was used to study how the hydrodynamic response of synthetic micro particles, i.e. silica beads, can be related to their physical properties and differ according to the fluid in which they are suspended. To compare the results obtained for the same kind of particles suspended in different fluids, the velocity signal $\mean{x}$ was computed per each experiment, by the DPIV-based algorithm described in \sect\ref{sec:method}.
